Exploration

### 2018-03-14 exploration.Rmd
added axis limits

sample.cells <- sample((1:n.cell)[lam.df$Surv.S>0], nPlots)
if(regPlots) {
  par(mfrow=c(3,2), mar=c(4,4,2,1))
  xx <- tibble(size=seq(U$lo, U$hi, length.out=100), size2=size^2, size3=size^3)
  E.t <- xx %>% add_column(yr=NA, s=NA, g=NA, fl=NA, seed=NA)
  xxx <- seq(0, U$hi*.5, length.out=100)
  for(i in sample.cells) {
    z.t <- data.frame(S$d[[i]]) %>% filter(!is.na(size) & yr==tmax)
    pt.col <- rgb(0,0,0,1/(nrow(z.t)^.25))
    E.t <- sim_expected(1, xx$size, 1:100, E.t, p, map(X, ~.[i,]), n_z)
    main.i <- paste("Cell", i)
    w1 <- Re(eigen(U$IPMs[,,i])$vectors[,1])[-1]; stable.dist1 <- w1/sum(w1)
    plot(surv~size, data=z.t, ylim=c(0,1), pch=20, col=pt.col,
         main=paste("Surv:", main.i), xlab="Size (t)", ylab="P(surv to t+1)")
      lines(E.t$size, E.t$s, col=2)
    plot(sizeNext~size, data=z.t, pch=20, col=pt.col, ylim=c(U$lo,U$hi),
         main=paste("Growth:", main.i), xlab="Size (t)", ylab="Size (t+1)")
      lines(E.t$size, E.t$g, col=2)
      abline(a=0, b=1, lty=2)
    plot(fl~size, data=z.t, pch=20, ylim=c(0,1), col=pt.col,
         main=paste("P(Flower):", main.i), xlab="Size (t)", ylab="P(flower)")
      lines(E.t$size, E.t$fl, col=2)
    plot(seed~size, data=z.t, pch=23-z.t$fl*3, col=pt.col, 
         ylim=range(c(E.t$seed, z.t$seed), na.rm=TRUE),
         main=paste("nSeeds:", main.i), xlab="Size (t)", ylab="Number of seeds")
      lines(E.t$size, E.t$seed, col=2)
    plot(U$y, stable.dist1, ylab="", type="l", col=2, 
         main=paste("Stable size distribution:", main.i), xlab="Size (t)")
    hist(with(S$d[[i]], sizeNext[is.na(size)]), col="grey", freq=F, 
         main=paste("Recruit sizes:", main.i), xlab="Recruit size (t+1)")
      lines(xxx, dnorm(xxx, p$rcr_z[1], p$rcr_z[2]), col="red")
  }
}
if(ipmPlots) {
  par(mfrow=c(2,2), mar=c(4,4,2,1))
  x <- c(0, U$y)
  for(i in sample.cells) {
   z.t <- data.frame(S$d[[i]]) %>% filter(!is.na(size) & yr==tmax)
   pt.col <- rgb(1,1,1,1/(nrow(z.t)^.25))
   main.i <- paste("Cell", i)
   z.t$y <- U$y[findInterval(z.t$size, U$y, all.inside=T)]
   totSd <- group_by(z.t, y) %>% summarise(seed=sum(seed, na.rm=T))
   image.plot(x, x, t(U$Ps[,,i]), main=paste("P matrix:", main.i), 
              xlab="Size (t)", ylab="Size (t+1)")
    points(sizeNext~size, data=z.t, col=pt.col, pch=20)
    abline(a=0, b=1, col="white", lty=2)
   image.plot(x, x, t(U$Fs[,,i]), main=paste("F matrix:", main.i), 
              xlab="Size (t)", ylab="Size (t+1)")
    points(totSd$y, totSd$seed/max(totSd$seed)*U$hi*.9, col="white", pch=20)
   image.plot(x, x, t(sens(U$IPMs[,,i])), main=paste("Sensitivity:", main.i), 
              xlab="Size (t)", ylab="Size (t+1)")
   image.plot(x, x, t(elas(U$IPMs[,,i])), main=paste("Elasticity:", main.i),
              xlab="Size (t)", ylab="Size (t+1)")
   points(sizeNext~size, data=z.t, col=pt.col, pch=20)
  }
}
par(mfrow=c(2,2), mar=c(4,4,2,1))
x <- c(0, U$y)
S_d <- map_dfr(S$d, data.frame) %>% sample_n(1000)
S_d$y <- U$y[findInterval(S_d$size, U$y, all.inside=T)]
totSd <- group_by(S_d, y) %>% summarise(seed=sum(seed, na.rm=T))
pt.col <- rgb(1,1,1,1/(nrow(S_d)^.25))
image.plot(x, x, t(apply(U$Ps, 1:2, mean)), main="P matrix: mean",
           xlab="Size (t)", ylab="Size (t+1)")
points(sizeNext~size, data=S_d, col=pt.col, pch=20)
image.plot(x, x, t(apply(U$Fs, 1:2, mean)), main="F matrix: mean",
           xlab="Size (t)", ylab="Size (t+1)")
points(totSd$y, totSd$seed/max(totSd$seed)*U$hi*.9, col="white", pch=20)
image.plot(x, x, sens(t(apply(U$IPMs, 1:2, mean))), main="Sensitivity: mean",
           xlab="Size (t)", ylab="Size (t+1)")
image.plot(x, x, elas(t(apply(U$IPMs, 1:2, mean))), main="Elasticity: mean",
           xlab="Size (t)", ylab="Size (t+1)")
points(sizeNext~size, data=S_d, col=pt.col, pch=20)

>>>>

sample.cells <- sample((1:n.cell)[lam.df$Surv.S>0], nPlots)
if(regPlots) {
  par(mfrow=c(3,2), mar=c(4,4,2,1))
  xx <- tibble(size=seq(U$lo, U$hi, length.out=100), size2=size^2, size3=size^3)
  E.t <- xx %>% add_column(yr=NA, s=NA, g=NA, fl=NA, seed=NA)
  xxx <- seq(0, U$hi*.5, length.out=100)
  for(i in sample.cells) {
    z.t <- data.frame(S$d[[i]]) %>% filter(!is.na(size) & yr==tmax)
    pt.col <- rgb(0,0,0,1/(nrow(z.t)^.25))
    E.t <- sim_expected(1, xx$size, 1:100, E.t, p, map(X, ~.[i,]), n_z)
    main.i <- paste("Cell", i)
    w1 <- Re(eigen(U$IPMs[,,i])$vectors[,1])[-1]; stable.dist1 <- w1/sum(w1)
    plot(surv~size, data=z.t, ylim=c(0,1), pch=20, col=pt.col, 
         xlim=c(U$lo, U$hi),
         main=paste("Surv:", main.i), xlab="Size (t)", ylab="P(surv to t+1)")
      lines(E.t$size, E.t$s, col=2)
    plot(sizeNext~size, data=z.t, pch=20, col=pt.col, ylim=c(U$lo,U$hi), 
         xlim=c(U$lo, U$hi),
         main=paste("Growth:", main.i), xlab="Size (t)", ylab="Size (t+1)")
      lines(E.t$size, E.t$g, col=2)
      abline(a=0, b=1, lty=2)
    plot(fl~size, data=z.t, pch=20, ylim=c(0,1), col=pt.col, xlim=c(U$lo, U$hi),
         main=paste("P(Flower):", main.i), xlab="Size (t)", ylab="P(flower)")
      lines(E.t$size, E.t$fl, col=2)
    plot(seed~size, data=z.t, pch=23-z.t$fl*3, col=pt.col, xlim=c(U$lo, U$hi),
         ylim=range(c(E.t$seed, z.t$seed), na.rm=TRUE),
         main=paste("nSeeds:", main.i), xlab="Size (t)", ylab="Number of seeds")
      lines(E.t$size, E.t$seed, col=2)
    plot(U$y, stable.dist1, ylab="", type="l", col=2, 
         main=paste("Stable size distribution:", main.i), xlab="Size (t)")
    hist(with(S$d[[i]], sizeNext[is.na(size)]), col="grey", freq=F, 
         main=paste("Recruit sizes:", main.i), xlab="Recruit size (t+1)")
      lines(xxx, dnorm(xxx, p$rcr_z[1], p$rcr_z[2]), col="red")
  }
}
if(ipmPlots) {
  par(mfrow=c(2,2), mar=c(4,4,2,1))
  x <- c(0, U$y)
  for(i in sample.cells) {
   z.t <- data.frame(S$d[[i]]) %>% filter(!is.na(size) & yr==tmax)
   pt.col <- rgb(1,1,1,1/(nrow(z.t)^.25))
   main.i <- paste("Cell", i)
   z.t$y <- U$y[findInterval(z.t$size, U$y, all.inside=T)]
   totSd <- group_by(z.t, y) %>% summarise(seed=sum(seed, na.rm=T))
   image.plot(x, x, t(U$Ps[,,i]), main=paste("P matrix:", main.i), 
              xlab="Size (t)", ylab="Size (t+1)")
    points(sizeNext~size, data=z.t, col=pt.col, pch=20)
    abline(a=0, b=1, col="white", lty=2)
   image.plot(x, x, t(U$Fs[,,i]), main=paste("F matrix:", main.i), 
              xlab="Size (t)", ylab="Size (t+1)")
    points(totSd$y, totSd$seed/max(totSd$seed)*U$hi*.9, col="white", pch=20)
   image.plot(x, x, t(sens(U$IPMs[,,i])), main=paste("Sensitivity:", main.i), 
              xlab="Size (t)", ylab="Size (t+1)")
   image.plot(x, x, t(elas(U$IPMs[,,i])), main=paste("Elasticity:", main.i),
              xlab="Size (t)", ylab="Size (t+1)")
   points(sizeNext~size, data=z.t, col=pt.col, pch=20)
  }
}
par(mfrow=c(2,2), mar=c(4,4,2,1))
x <- c(0, U$y)
S_d <- map_dfr(S$d, data.frame) %>% sample_n(1000)
S_d$y <- U$y[findInterval(S_d$size, U$y, all.inside=T)]
totSd <- group_by(S_d, y) %>% summarise(seed=sum(seed, na.rm=T))
pt.col <- rgb(1,1,1,1/(nrow(S_d)^.25))
image.plot(x, x, t(apply(U$Ps, 1:2, mean)), main="P matrix: mean",
           xlab="Size (t)", ylab="Size (t+1)")
points(sizeNext~size, data=S_d, col=pt.col, pch=20)
image.plot(x, x, t(apply(U$Fs, 1:2, mean)), main="F matrix: mean",
           xlab="Size (t)", ylab="Size (t+1)")
points(totSd$y, totSd$seed/max(totSd$seed)*U$hi*.9, col="white", pch=20)
image.plot(x, x, sens(t(apply(U$IPMs, 1:2, mean))), main="Sensitivity: mean",
           xlab="Size (t)", ylab="Size (t+1)")
image.plot(x, x, elas(t(apply(U$IPMs, 1:2, mean))), main="Elasticity: mean",
           xlab="Size (t)", ylab="Size (t+1)")
points(sizeNext~size, data=S_d, col=pt.col, pch=20)
